---
title: "R Notebook"
output: html_notebook
---

```{r}

df <- read_delim('cereal.csv', delim = ';')
```

## Questions

1.  What are the top 5 rated cereals?

2.  Which manufacturer has the highest average rating?

3.  Which cereals have high calories?

4.  Which cereals have low calories?

5.  How do cereals with low sugar and high fiber compare in terms of rating?

6.  Are hot cereals better rated than cold cereals?

7.  How many hot cereals are there compared to cold cereals?

    ```{r}
    df <- df[-1,]

    ```

    ```{r}

    df[-(1:3)] <- lapply(df[-(1:3)], function(x) as.numeric(as.character(x)))


    ```

    ```{r}
    colnames(df)
    ```

    ```{r}


    top_5<- select(df, name, rating ,mfr)%>%
      arrange(desc(rating))%>%
      slice(1:5)
    top_5

    #top 5 rated cereals are:

    #All-Bran with Extra Fiber
    #Shredded Wheat 'n'Bran
    #Shredded Wheat spoon size
    #100% Bran

    #from top 5, 4 are from Nabisco and one from kellogs
    ```

```{r}
ggplot(data = top_5, mapping = aes(x=rating , y = name , fill = mfr))+
  geom_bar(stat = "identity")
```

####  A = American Home Food Products; G = General Mills; K = Kelloggs; N = Nabisco; P = Post; Q = Quaker Oats; R = Ralston Purina.

```{r}
group_by(df, mfr)%>%
  summarise(
    avg_cal =mean(calories)
  )%>%
  arrange(avg_cal)

#Arranging mfr with calories low to hight:
#Nabisco
#Quaker Oats
#American Home Food Products
#Kelloggs
#Post
```

```{r}
mfr <- group_by(df, mfr)%>%
  summarise(avg_rating = mean(rating),
            avg_cal = mean(calories))%>%
  arrange(desc(avg_rating))

mfr

#top 5 avg.rating manufacturar 

#Nabisco
#American Home Food Products
#Kelloggs
#Quaker Oats
#Post
```

```{r}
mfr <- gather(mfr,event, avg,avg_rating:avg_cal)
mfr
```

```{r}
ggplot(mfr, aes(x=mfr, y= avg ,fill= event))+
  geom_bar(stat = 'identity', position = 'dodge')
```

```{r}

arrange(df, calories)

#top 5 low calories cereals:

#All-Bran with Extra
#Puffed Rice
#Puffed Wheat
#100% Bran
#All-Bran
```

```{r}
View(arrange(df, desc(calories)))

#High calories ceresls:

#Mueslix Crispy Blend
#Muesli Raisins, Dates, & Almonds
#Muesli Raisins, Peaches, & Pecans
#Just Right Fruit & Nut
#Nutri-Grain Almond-Raisin
```

```{r}
ggplot(data =df, mapping = aes(x= calories, y = rating, color = 'red' ))+
  geom_point()

# Most cereals have values between 80-120.
# Cereals with low calories are rated higher.
# Cereals with high calories are rated lower.

```

#### fiber & sugar

```{r}
summarise(df, 
          fiber = mean(fiber, na.rm =TRUE),
          sugar = mean(sugars, na.rm =TRUE))

#Avg, value of fiber and sugar
```

```{r}
summarise(df, rating =mean(rating))

#Average Rating for All Cereals
```

```{r}
filter(df, fiber>2 , sugars <7)%>%
  summarise(
    rating = mean(rating)
  )

# when fiber is more than avg and sugar is less than avg.
# than the avg. rating comes out to be better than whole group
```

```{r}
ggplot(df, mapping = aes(x= sugars, y = rating, color = mfr))+
  geom_point(stat = "identity")

# The graph shows that low sugar leads to higher ratings, and as sugar increases, ratings decrease.

```

```{r}
ggplot(df, mapping = aes(x= sugars, y = calories, color = mfr))+
  geom_point(stat = "identity")

# The graph shows that the most common calorie count in cereal is between 80-120, and many companies can achieve the same calories with lower sugar.

```

#### hot and cold

```{r}

HandC<- group_by(df, type)%>%
  summarise(
    avg.rating = mean(rating),
    count=n()
  )
HandC
#out of 80 cereal only 3 are hot cereal rest are cold
```

```{r}
ggplot(HandC, mapping = aes(x='',y = count, fill = type))+
  geom_bar(stat = 'identity', width = 1)+
  coord_polar("y",start = 0)
```

### Hypotheses

-   **Top Rated Cereals**:

    -   The top 5 rated cereals are primarily from Nabisco, indicating Nabisco's consistent production of high-quality cereals.

-   **Calories and Manufacturer**:

    -   Nabisco produces cereals with the lowest calorie content compared to other manufacturers.

-   **Average Rating by Manufacturer**:

    -   Nabisco leads in average cereal ratings, followed by American Home Food Products, Kellogg's, Quaker Oats, and Post.

-   **Calorie Content and Ratings**:

    -   Low calorie cereals are rated higher, while high calorie cereals are rated lower.

-   **Fiber and Sugar Content**:

    -   Cereals with higher fiber and lower sugar content have better ratings than the overall average.

-   **Sugar Content and Ratings**:

    -   Lower sugar content correlates with higher ratings.

-   **Calorie Count Distribution**:

    -   Most cereals have 80-120 calories, and those with lower sugar content in this range are rated higher.

-   **Hot vs. Cold Cereals**:

    -   Only 3 out of 80 cereals are hot cereals, with no significant rating difference between hot and cold cereals.
